Exercise 3: Software Architecture in Practice Case: Beer Web Store

### 2008-03-17 trunk/SAiP/Module1/H3/doc/architecturaldescription.tex
Should -> Must

The domain model accesses the database through the database facade
when needed. This can be expressed in another sequence diagram.
Sequence diagrams showing the checkout including payment should
also be made.

@@

Working as an developer/tester/engineer means that everything must be quantifiable in some way, and box-and-line drawings do not offer this unambigious quantifiability. For this a clearly defined modeling language, without ambiguity as to the meaning of the model, is needed. An example of such a language is Unified Modelling Language(UML), which would allow the box-and-line drawing to be represented as one or more diagrams solving all the ambiguaty of the box-and-line drawing with only a single requirement; one must know the language, which is indeed one of the reasons while box-and-line drawings are still widely used - there is no single unambigious modelling language known by all stakeholders, and when that is the case it may be more confusing then benificial to spend time making sure the diagram is clear and unambigious, if that clarity is derived from symbolic notation that the readers (stakeholders) do not understand.

\subsection{Architectural Description - Question 4}

\begin{question}
Discuss what architectural description would be needed if
the system was to be realized as a Service-Oriented Architecture
\end{question}

>>>>

The domain model accesses the database through the database fa\c ade
when needed. This can be expressed in another sequence diagram.
Sequence diagrams showing the checkout including payment must
also be made.

@@

Working as an developer/tester/engineer means that everything must be quantifiable in some way, and box-and-line drawings do not offer this unambiguous quantifiable. For this a clearly defined modelling language, without ambiguity as to the meaning of the model, is needed. An example of such a language is Unified Modelling Language(UML), which would allow the box-and-line drawing to be represented as one or more diagrams solving all the ambiguity of the box-and-line drawing with only a single requirement; one must know the language, which is indeed one of the reasons while box-and-line drawings are still widely used - there is no single unambiguous modelling language known by all stakeholders, and when that is the case it may be more confusing then beneficial to spend time making sure the diagram is clear and unambiguous, if that clarity is derived from symbolic notation that the readers (stakeholders) do not understand.

\subsection{Architectural Description - Question 4}
\label{sec:ad_q4}
\begin{question}
Discuss what architectural description would be needed if
the system was to be realized as a Service-Oriented Architecture
\end{question}
